Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
Started rewroding Methodology

\section{Methodology}
Our survey was conducted in multiple parts. The first section of the survey consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies). The next section of questions consisted of questions regarding individual and situational smartphone concerns, which were questions more familiar to our participant base and are used for calibrating results. The following section of the survey consisted of risk and benefit assessment of technologies, where participants were asked to consider general, multi-situational concerns regarding specific technologies. The final section of the survey consisted of demographics questions on basic information, privacy concerns, and wearable device ownership. Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.51\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 14.91\% \\

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
<data> & VUR  \\
social security number & 98.04\% \\
a video of you unclothed & 97.44\% \\
bank account information & 97.10\% \\
recordings of your work conversations & 96.97\% \\
an incriminating/embarrassing photo of you & 96.36\% \\
a photo of you unclothed & 96.30\% \\
credit card information & 95.92\% \\
username and password for websites & 95.41\% \\
a video of you entering in your PIN & 93.91\% \\
recordings of your phone conversations & 93.88\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
bank account information & 90.91\% \\
a video of you unclothed & 90.62\% \\
social security number  & 88.68\% \\
video of you entering your PIN & 88.57\% \\
an incriminating/embarrassing photo of you & 78.05\% \\
a photo of you unclothed & 77.78\% \\
a video of you entering a passcode to a door & 75.00\% \\
when and how much you have sex & 73.08\% \\
an incriminating/embarrassing video of you & 71.88\% \\
a random (inward-facing) photo of you at home & 66.67\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
your name & 47.25\% \\
when and how much you exercise & 46.07\% \\
when you were happy or having fun & 38.10\% \\
what television shows you watch & 35.96\% \\
when you are busy or interruptible & 34.34\% \\
your heart rate & 32.28\% \\
music from your device & 31.87\% \\
your age & 29.67\% \\
the language you speak & 20.95\% \\
your gender & 16.81\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedbottom10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
when and how much you exercise & 16.67\% \\
how much you use your phone & 15.79\% \\
your age & 14.29\% \\
how much you like the people you interact with & 13.79\% \\
when, what, and how much you ate & 12.50\% \\
which television shows you watch & 11.43\% \\
your gender & 9.52\% \\
your heart rate & 9.09\% \\
eye movement patterns (for eye tracking) & 6.98\% \\
the language you speak & 2.50\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedbottom10}
\end{center}
\end{table}

>>>>

\section{Methodology}
Our survey consisted of multiple parts. The first section consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the ``Cubetastic3000.'' We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media). The next set of questions focused on individual and situational smartphone concerns. These questions focused on the same scenarios, but we substituted smartphones for wearable technologies in order to see whether participants familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). The next section of the survey involved performing overall risk/benefit rankings of various wearable technologies relative to better understood technologies. Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices. Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.51\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 14.91\% \\

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
<data> & VUR  \\
social security number & 98.04\% \\
a video of you unclothed & 97.44\% \\
bank account information & 97.10\% \\
recordings of your work conversations & 96.97\% \\
an incriminating/embarrassing photo of you & 96.36\% \\
a photo of you unclothed & 96.30\% \\
credit card information & 95.92\% \\
username and password for websites & 95.41\% \\
a video of you entering in your PIN & 93.91\% \\
recordings of your phone conversations & 93.88\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedtop10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
bank account information & 90.91\% \\
a video of you unclothed & 90.62\% \\
social security number  & 88.68\% \\
video of you entering your PIN & 88.57\% \\
an incriminating/embarrassing photo of you & 78.05\% \\
a photo of you unclothed & 77.78\% \\
a video of you entering a passcode to a door & 75.00\% \\
when and how much you have sex & 73.08\% \\
an incriminating/embarrassing video of you & 71.88\% \\
a random (inward-facing) photo of you at home & 66.67\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedtop10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
your name & 47.25\% \\
when and how much you exercise & 46.07\% \\
when you were happy or having fun & 38.10\% \\
what television shows you watch & 35.96\% \\
when you are busy or interruptible & 34.34\% \\
your heart rate & 32.28\% \\
music from your device & 31.87\% \\
your age & 29.67\% \\
the language you speak & 20.95\% \\
your gender & 16.81\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedbottom10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
when and how much you exercise & 16.67\% \\
how much you use your phone & 15.79\% \\
your age & 14.29\% \\
how much you like the people you interact with & 13.79\% \\
when, what, and how much you ate & 12.50\% \\
which television shows you watch & 11.43\% \\
your gender & 9.52\% \\
your heart rate & 9.09\% \\
eye movement patterns (for eye tracking) & 6.98\% \\
the language you speak & 2.50\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedbottom10}
\end{center}
\end{table}
